Meta-analysis

### 2020-02-05 05_MetaAnalysis.Rmd
couple of edits corrections

efficacy %>% 
   ggplot(aes(Treatment, Mean))+
   geom_hline(yintercept = c(0.8,1,1.2,1.4), color = "grey80", linetype = 3)+
   geom_point(aes(size=1/SE), shape=15)+
   geom_linerange(aes(ymin = CIinf, ymax = CIsup))+
   coord_flip()+
   theme_usq()

@@

```{r LMER_finalSev}

@@

@@

>>>>

efficacy %>% 
   ggplot(aes(Treatment, Mean))+
   geom_hline(yintercept = c(0.8,1,1.2,1.4), color = "grey80", linetype = 3)+
   geom_point(aes(size=1/SE), shape=15)+
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper))+
   coord_flip()+
   theme_usq()

@@

coef(Me_mod2)
```

Lets compare the area under the disease progress curve (AUDPC) to final severity.
```{r LMER_finalSev}

@@

anova(Me_mod3, Me_mod4)

@@

Final severity as a measurement does not model as well as AUDPC. Also it is less significant of a predictor.
